A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-08-05 paper.tex
Minor fixes

With the functionalities of Ethereum smart contracts, a flexible and verifiable trading mechanism can be achieved. In our system, \textbf{Product Contract} is made for the product launching and subscribing. The information of data products such as address of the data provider, subscription fee, brokerage fee, threshold of consent votes of refunding, MAM channel/endpoint ID (the data entry point), time period and the broker-verified encryption key are listed on Product Contract. Listing. \ref{lst:constructor} list the data fields of Product Contract, and Fig.~\ref{fig:smart_contract_mam} shows the relationship of Product Contract and MAM. Furthermore, the participants can exchange encryption keys without any authorities via smart contracts. Though this design may cost extra transaction fees than exchanging key off-chain, it is considered a more secure strategy to protect the privacy of participants that only the DID document address and Ethereum addresses are revealed during the subscription process. Binding trading and data storage to smart contract ensures consumers can always retrieve the encryption key from the Product Contract once they pay.

@@

\section{Masked Authenticated Messaging}
\label{section:MAM}
MAM enables broadcasting encrypted and authenticated data stream, referring as channel, on the Tangle. The publisher publishes messages that are propagated through the network and can be accessed by the subscribers only. With MAM, the rights of data access are traded instead of a copy of data in the trading platform, which eliminates the need for data consumers to have additional storage.
Section.~\ref{section:mam_streams} to ~\ref{section:mam_features} explain the structure, fuctions and features of MAM, and our proposed MAM delegation mechanism  is clarified in Section.~\ref{section:ta_endpoint}.

>>>>

With the functionalities of Ethereum smart contracts, a flexible and verifiable trading mechanism can be achieved. In our system, \textbf{Product Contract} is made for the product launching and subscribing. The information of data products such as address of the data provider, subscription fee, brokerage fee, threshold of consent votes of refunding, MAM channel/endpoint ID (the data entry point), time period and the broker-verified encryption key are listed on Product Contract. Listing. \ref{lst:constructor} list the data fields of Product Contract, and Fig.~\ref{fig:smart_contract_mam} shows the relationship of Product Contract and MAM.

Furthermore, the participants can exchange encryption keys without any authorities via smart contracts. Though this design may cost extra transaction fees than exchanging key off-chain, it is considered a more secure strategy to protect the privacy of participants that only the DID document address and Ethereum addresses are revealed during the subscription process. Binding trading and data storage to smart contract ensures consumers can always have access after payment, even if the key is lost, and providers can track and manage the authorized user list.

@@

\section{Masked Authenticated Messaging}
\label{section:MAM}
MAM enables broadcasting encrypted and authenticated data stream, referring as channel, on the Tangle. The publisher publishes messages that are propagated through the network and can be accessed by the subscribers only. With MAM, the rights of data access are traded instead of a copy of data in the trading platform, which eliminates the need for data consumers to have additional storage.
Section.~\ref{section:mam_streams} to ~\ref{section:mam_features} explain the structure, fuctions and features of MAM proposed by IOTA Foundation, and our proposed MAM delegation mechanism is clarified in Section.~\ref{section:ta_endpoint}.
